The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-27 article/article.tex
witness trees

\section{Analysis}
\label{sec:analysis}
In this section, we will prove Theorems \ref{theorem:greedy}, \ref{theorem:agln} and \ref{theorem:algm} in detail, using \emph{witness trees} to provide an upper bound for the event that a bin contains too many balls. We will prove the bounds for $m=n$ for both the Greedy and the Always-go-left scheme in Sections \ref{sec:witnessGreedy} and \ref{sec:AlwaysGoLeft} respectively. However, we use some simplifying assumptions in those two sections to provide a more clear presentation of the proof techniuqe. Section \ref{sec:nondistinctBalls} will extend these proofs to remove the simplifying assumptions we made initially. Section \ref{sec:moreBalls} will extend the proof to cover the heavily loaded case where $m > n$ as well.

>>>>

\section{Analysis}
\label{sec:analysis}
In this section, we will prove Theorems \ref{theorem:greedy}, \ref{theorem:agln} and \ref{theorem:algm} in detail, using \emph{witness trees} to provide an upper bound for the event that a bin contains too many balls.

When the maximum load exceeds some given threshold value we say that a \emph{bad event} occurs and construct an \emph{activated witness tree}, i.e., the activation of a witness tree is implied by a bad event. The probability for the existance of an activated witness tree upper-bounds the probability that a bad event occurs.

We will prove the bounds for $m=n$ for both the Greedy and the Always-go-left scheme in Sections \ref{sec:witnessGreedy} and \ref{sec:AlwaysGoLeft} respectively. However, we use some simplifying assumptions in those two sections to provide a more clear presentation of the proof techniuqe. Section \ref{sec:nondistinctBalls} will extend these proofs to remove the simplifying assumptions we made initially. Section \ref{sec:moreBalls} will extend the proof to cover the heavily loaded case where $m > n$ as well.
